心理ネットワーク入門１：横断データ

### 2021-10-11 how-to-psychological-network1.Rmd
update

```{r message=FALSE, warning=FALSE}
library(NetworkComparisonTest)
res_nct <- NCT(network_male, network_female, test.edges=TRUE, test.centrality=TRUE)
```

>>>>

```{r message=FALSE, warning=FALSE}
library(NetworkComparisonTest)
res_nct <- NCT(network_male, network_female, progressbar=FALSE, test.edges=TRUE, test.centrality=TRUE)
```
